Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2022-10-28 analysis/paper/paper.Rmd
Remove figures from resulting doc
Having this results in duplicated figures in the proofs for review

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fit to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper. Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. No article scored 3 for data availability. Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_1.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_3.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_4.eps"))
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_5.eps"))
```

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  options = "-dEPSCrop"
)

include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
```

>>>>

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fit to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper. Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. No article scored 3 for data availability. The fitness was found to be good for all models.", cache=FALSE, fig.env='figure'}

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  options = "-dEPSCrop"
)
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_3.eps"),
  options = "-dEPSCrop"
)
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_4.eps"),
  options = "-dEPSCrop"
)
```

@@

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  plot = ggdraw(p),
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_5.eps"),
  options = "-dEPSCrop"
)
```

@@

rsvg_ps(svg = charToRaw(p),
        file = here("analysis/figures/Sparks_et_al_Figure_6.eps"))
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_6.eps"),
  options = "-dEPSCrop"
)
```
